\normalfont \normalsize \textsc{UNSW School of Computer Science and Engineering} \\ [24pt] \horrule{1pt} \\[0.5cm] \LARGE Word Embedding and Question Answering \\ \horrule{1pt} \\[0.5cm]

### 2019-12-11 paper.tex
BERT: input/output representation

\subsubsection{Transformer}
\subsubsection{Masked Language Model}
 \begin{figure}
  \includegraphics[scale=0.53]{bertinput.png}
  \caption{BERT input representation. The input embeddings are the sum of the token embeddings, the segmentation embeddings and the position embeddings.}
  \label{fig:skip-gram}
\end{figure}
\section{Question Answering}

>>>>

In this report, we denote the number of layers, aka, Transformer Blocks, as $L$.\\
The hidden size as $H$. \\
The number of self-attention heads as $A$. 
\subsubsection{Transformer}
\subsubsection{Input/Output Representation}
The input of \textbf{BERT} can be both a sentence or a set of sentences, which is an arbitrary continuous text. \\\\
Then \textbf{BERT} uses WordPiece embeddings with a 30,000-token library. The first token of every sequence is always a  special classification token (\texttt{[CLS]}). The final hidden state corresponding to this token is used as the aggregate sequence representation for classification tasks. Sentence pairs are packed together into a single sequence. \textbf{BERT} differentiate the sentences in two ways. \\\\
 First, we separate them with a special token (\texttt{[SEP]}). Second, we add a learned embedding to every token indicating whether it belongs to sentence \texttt{A} or sentence \texttt{B}. \\\\
 As shown in \textbf{Figure 14}, we denote the input embedding as \texttt{E}, the final hidden vector of the special \texttt{[CLS]} for the $i$-th input token as $T_i \in \mathbb{R}$
\subsubsection{Masked Language Model}
  \includegraphics[scale=0.53]{bertinput.png}
  \caption{BERT input representation. The input embeddings are the sum of the token embeddings, the segmentation embeddings and the position embeddings.}
\section{Question Answering}
